

::: {.calbox}
calbox Make sure you have installed `PsychoPy` on your own computer from this link before attempting the challenges:

* [**PsychoPy download**](https://www.psychopy.org/download.html)
:::


::: {.rmdnote}
rmdnote Make sure you have installed `PsychoPy` on your own computer from this link before attempting the challenges: [**PsychoPy download**](https://www.psychopy.org/download.html)
:::

:::: {.blackbox}
::: {.center}
**NOTICE!**
:::

blackbox Make sure you have installed `PsychoPy` on your own computer from this link before attempting the challenges: [**PsychoPy download**](https://www.psychopy.org/download.html)
::::


This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a math equation $a^2 + b^2 = c^2$.

## Usage

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


:::: {.greybox}
::: {.center}
**LAST YEARS CHALLENGES (OPENSESAME)**
:::
* Team challenges (OpenSesame)
  1. Change the buttons for “old” and “new” from Z and M to the left (old) and right (new) arrow keys.
  2. Add feedback on every trial.
::::

